Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
done up to conclusion

The same observations are made for the MFCCs for a $k\leq5$. However for a rank $k$ greater than 5, there is no clear evidence that \emph{ob-c} and \emph{ob-w} approaches improve the results compared to \emph{early}. The latter even outperform \emph{ob-a} for $k\geq5$.

From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This may be due to the fact that, at some point, the MFCCs fail to dissociate the discriminative events of a scene from the non-informative ones, thus making a centroid-based description useless, or even counterproductive when the centroids are not weighted/selected.

@@

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to segregate distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none of them managed to outperform the baseline strategy in temporal integration, namely majority voting. Among object-based methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, and reaches a accuracy of $66\% \pm0.7$.

\ml{explain why ?}

>>>>

The same observations are made for the MFCCs for a $k\leq5$. However for a rank $k$ greater than 5, there is no clear evidence that \emph{ob-c} and \emph{ob-w} approaches improve the results compared to \emph{early}. The latter even outperform \emph{ob-a} for $k\geq5$. From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This may be due to the fact that, at some point, the MFCCs fail to dissociate the discriminative events of a scene from the non-informative ones, thus making a centroid-based description useless, or even counterproductive when the centroids are not weighted/selected.

@@

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to segregate distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none of them managed to outperform the baseline strategy in temporal integration, namely majority voting. Among object-based methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, and reaches a accuracy of $66\% \pm0.7$. This might be due to the fact that the discriminability gained by the object-based approach is already gained by the classifiers during the training and the fact that considering the object-base approach resort to considering an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size, see discussion in Section \ref{sec:eili}.
